---
title: "CodeBook For courseproject of Getting and Cleaning Data"
Purpose: To describe the variables, data, and the logic in transforming source data to tidy data
Author: Vijji Sekuboyina
---

###Source Data:
Data for the project is taken from:
https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip 

###Description of Data:
The source data collected from the accelerometers from the Samsung Galaxy S smartphone. A full description is available at the site where the data was obtained:

http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones 

### Data set Information:

* features.txt - Contains the labels for the 564-features 
* activity_labels.txt - Contains the 6 activities that were monitored to collect the data [1-WALKING, 2-WALKING_UPSTAIRS, 3-WALKING_DOWNSTAIRS, 4-SITTING, 5-STANDING, 6-LAYING]
* train/X_train.txt - Data for 564-features for which the labels are in features.txt
* train/subject_train.txt - Each row shows the subject that collected the data in corresponding row of X_train.txt
* train/y_train.txt - Each row shows the activity that was performed which resulted in the data in the corresponding row of X_train.txt
* test/X_test.txt - Data for 564-features for which the labels are in features.txt
* test/subject_test.txt - Each row shows the subject that collected the data in corresponding row of X_test.txt
* test/y_test.txt - Each row shows the activity that was performed which resulted in the data in the corresponding row of X_test.txt

### Varaibles used:

* FeaturesTbl - Table that contained information from features.txt
* SubTrainTbl - Table that stored information of the subject id for training data
* xTrainTbl - Table with data for 564-variables obtained for training
* yTrainTbl - Table with activity information for training data
* SubTestTbl - Table that stored information of the subject id for testing data
* xTestTbl - Table with data for 564-variables obtained for testing
* yTestTbl - Table with activity information for testing data

## Steps performed for Cleaning data
S1: Gather all Training information: 
    Merge the three tables - yTrainTbl, SubTrainTbl and xTrainTbl [Using cbind]
    
    *TrainingTbl <- cbind (yTrainTbl, SubTrainTbl, xTrainTbl)*
    
S2: Gather all Testing information:
    Merge the three tables - yTestTbl, SubTestTbl and xTestTbl [Using cbind]
    
    *TestTbl <- cbind (yTestTbl, SubTestTbl, xTestTbl)*
    
S3: Merge both Training information and testing information into one big table

    *AllDataTbl <- rbind (TrainingTbl, TestTbl)*
    
S4: Extract information only that pertains to mean and standard deviation.
    i.e., identify the columns that have mean and std in their names and extract them
    Extract the subject and activyt information also
    
    *DataMeanStd <- AllDataTbl[, grepl("Subject|ActID|mean|std", LabelNames)]*
    
S5: Give a descriptive Activity name in the resulting table
    Read the activity information from the activity data and add a new column
    for activity in the above table
    
    *DataMeanStd$Activity <- ActivityTbl [DataMeanStd$ActID, 2]*
    
S6: Appropriately label the column names to have descriptive names:
    For this, replace mean() with Mean, std() with Std Deviation, etc
```{r}
#   DataLabels <- colnames (DataMeanStd)
#   for (i in 1:length(DataLabels)) {
#      DataLabels[i] <- gsub("-mean\\()", " Mean", DataLabels[i])
#      DataLabels[i] <- gsub("-std\\()", " Std Deviation", DataLabels[i]) 
#      DataLabels[i] <- gsub("-meanFreq\\()", " Mean Frequency", DataLabels[i])
#      DataLabels[i] <- gsub("^t", "Time: ", DataLabels[i])
#      DataLabels[i] <- gsub("^f", "Freq: ", DataLabels[i])
#      DataLabels[i] <- gsub("Acc", " Accelaration", DataLabels[i])
#      DataLabels[i] <- gsub("BodyBody", "Body", DataLabels[i])
#      DataLabels[i] <- gsub("Mag", " Magnitude", DataLabels[i])
#      DataLabels[i] <- gsub("Gyro", " Gyro", DataLabels[i])
#      DataLabels[i] <- gsub("Jerk", " Jerk", DataLabels[i])
#   }
#   colnames(DataMeanStd) <- DataLabels
```

S7: From the data set in step 6, creates a second, independent tidy data
    set with the average of each variable for each activity and each subject.
    For this we use ddply and numcolwise function

    *TidyDataWithAvgs <- ddply(DataMeanStd, c("Subject", "Activity"), 
                              numcolwise(mean))
     write.table (TidyDataWithAvgs, file="tidydatawithaverages.txt")*
     
```{r}

```